### 2014-06-06 paper/body.tex
table caption edits

\begin{table}[t]
\caption{Convolutional Network architecture sizes and hyperparameters. \todo{explain what R vs. S is}}
\label{tab:network_architecture}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|l|l|l|}
\hline
       &      & filter & number  &        &        &     &         & Maxpool        & LRN (size,        \\
name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & $\alpha$,$\beta$) \\
\hline
conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[t]
\caption{Parameter initializations and learning rates}
\label{tab:learning_hyperparams}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|}
\hline
       & \multicolumn{3}{c|}{\bf Weight}     &  \multicolumn{3}{c|}{\bf Bias}       \\
\cline{2-7}
       & gaus   & LR-mult & decay &  const  & LR  & decay \\
\hline
conv1  & .01    & 1       & y     &  0      & 2   & n     \\
conv2  & .01    & 1       & y     &  1      & 2   & n     \\
conv3  & .01    & 1       & y     &  0      & 2   & n     \\
conv4  & .01    & 1       & y     &  1      & 2   & n     \\
conv5  & .01    & 1       & y     &  1      & 2   & n     \\
fc6    & .005   & 1       & y     &  1      & 2   & n     \\
fc7    & .005   & 1       & y     &  1      & 2   & n     \\
fc8    & .01    & 1       & y     &  0      & 2   & n     \\ 
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{table}[t]
\caption{Convolutional Network architecture sizes and hyperparameters. Conv stands for Convolutional layers. FC stands for fully-connected layers. R/S indicates that the layer consists of rectilinear or sigmoidal neurons. Neurons in dropout layers fail to fire with 50\% probability \todo{accurate?} \citep{Hinton-et-al-arxiv2012}\todo{Do we need to explain what groups means? Stride?} LRN stands for local response normalization \citep{Krizhevsky-2012}.}
\label{tab:network_architecture}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|l|l|l|}
\hline
       &      & filter & number  &        &        &     &         & Maxpool        & LRN (size,        \\
name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & $\alpha$,$\beta$) \\
\hline
conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[t]
\caption{Parameter initializations and learning rates. \todo{JY: I expanded the table headings (we have the space). Please check that I did so accurately. I had to guess on most.}}
\label{tab:learning_hyperparams}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|}
\hline
       & \multicolumn{3}{c|}{\bf Weight}     &  \multicolumn{3}{c|}{\bf Bias}       \\
\cline{2-7}
       & Gaussian Std. Dev.   & Local Response-multiplier & decay &  const  & Local Response  & decay \\
\hline
conv1  & .01    & 1       & y     &  0      & 2   & n     \\
conv2  & .01    & 1       & y     &  1      & 2   & n     \\
conv3  & .01    & 1       & y     &  0      & 2   & n     \\
conv4  & .01    & 1       & y     &  1      & 2   & n     \\
conv5  & .01    & 1       & y     &  1      & 2   & n     \\
fc6    & .005   & 1       & y     &  1      & 2   & n     \\
fc7    & .005   & 1       & y     &  1      & 2   & n     \\
fc8    & .01    & 1       & y     &  0      & 2   & n     \\ 
\hline
\end{tabular}
\end{center}
\end{table}
